### 2017-11-09 paper/sections/1_introduction.tex
paper: 1st draft
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Our analysis of the key-value activity generated by the ParSplice molecular
dynamics simulation demonstrates the need for more complex cache management
strategies. Baseline measurements show clear keyspace access patterns and hot
spots that offer significant opportunity for optimization. We use the data
management and policy engine from the Mantle system to dynamically explore a
variety of techniques, ranging from basic algorithms and heuristics to
statistical models, calculus, and machine learning. While Mantle was originally
designed for distributed file systems, we show how the collection of
abstractions effectively decomposes the problem into manageable policies for a
different domain and service (in this case, cache management).  Our exploration
of this space results in a two policy scheme that achieves 96\% efficiency
while using only 7.6\% of the memory resources required by the base case.

@@

The fine-grained data annotation capabilities provided by key-value storage is
a natural match for many types of scientific simulation. Simulations relying on
a mesh-based decomposition of a physical region may result in millions or
billions of mesh cells. Each cell contains materials, pressures, temperatures
and other characteristics that are required to accurately simulate phenomena of
interest. In our target application, the
ParSplice~\cite{perez:jctc20150parsplice} molecular dynamics simulation, a
hierarchy of cache nodes and a single node key-value store are used to store
both observed minima across a molecule's equation of motion (EOM) and the
hundreds or thousands of partial trajectories calculated each second during a
parallel job. Unfortunately, if we scale the system the IO to the storage
hierarchy will quickly saturate both the storage and bandwidth capacity of a
single node, so we need more effective data management techniques, such as
cache management or load balancing across a cluster.

@@

In this paper, we design cache management policies for the ParSplice worker
node, driven by a detailed analysis of the application's key-value accesses
over the course of a long running simulation across a variety of initial
conditions.  This type of analysis helps the system scale by (1) showing the
capacity and resource requirements of a single node and (2) informing the
design of load balancing policies for when we switch to a distributed key-value
store back-end to store EOM minima.  For example,
Figure~\ref{fig:motivation-regimes} shows the cache activity of a ParSplice
node and demonstrates that small changes to the rates at which new atoms enter
the simulation (\(\Delta\)) can have a strong effect on the timing and
frequency with which new EOM minima are discovered and referenced.  The
ParSplice caches on each node are trimmed when memory pressure reaches a
threshold but the number of unique keys accessed (black points along bottom of
both graphs) in Figure~\ref{fig:motivation-regimes} suggests that a small cache
of EOM minima should be sufficient.

% What is Mantle
We use the data management language and policy engine from the Mantle
paper~\cite{sevilla:sc15-mantle} to dynamically explore the effects of
different cache management strategies for the changing key-value workloads
generated by ParSplice.  Mantle was originally labeled a programmable file
system metadata load balancer, but we realize now that the collection of
abstractions was a control plane that improved metadata access. So in this
paper we refer to Mantle as a policy engine that injects policies written in
our data management language directly into a running service ({\it e.g.} file
system, key-value store, application).  We show how this approach is useful for
reasoning about and designing different cache management strategies.
Developers write policies for ``when" they want data moved and ``how much" of
the data to move, then the framework executes these policies whenever a
decision needs to be made.  These abstraction help developers unfamiliar with
the domain quickly reason about, develop, and deploy new policies that control
temporal and spatial locality. We show that Mantle:

@@

This last contribution is explored in
Sections~\S\ref{sec:cache-management-using-system-archiecture-knowledge}
and~\S\ref{sec:cache-management-using-domain-specific-knowledge}, where we try
a range of policies from different disciplines; but more importantly, in
Section~\S\ref{sec:relation-to-file-systems}, we conclude that the collection
of policies we designed for ParSplice's cache management are very similar to
the policies in the Ceph file system that are used to load balance metadata,
suggesting that there is potential for automatically adapting and generating
policies dynamically.

>>>>

Our analysis of the key-value activity generated by the ParSplice molecular
dynamics simulation demonstrates the need for more complex cache management
strategies. Baseline measurements show clear keyspace access patterns and hot
spots that offer significant opportunity for optimization. We use the data
management and policy engine from the Mantle system to dynamically explore a
variety of techniques, ranging from basic algorithms and heuristics to
statistical models, calculus, and machine learning. While Mantle was originally
designed for distributed file systems, we show how the collection of
abstractions effectively decomposes the problem into manageable policies for a
different domain and service.  Our exploration of this space results in a two
policy scheme that achieves 96\% efficiency while using only 7.6\% of the
memory resources required by the base case.

@@

The fine-grained data annotation capabilities provided by key-value storage is
a natural match for many types of scientific simulation. Simulations relying on
a mesh-based decomposition of a physical region may result in millions or
billions of mesh cells. Each cell contains materials, pressures, temperatures
and other characteristics that are required to accurately simulate phenomena of
interest. In our target application, the
ParSplice~\cite{perez:jctc20150parsplice} molecular dynamics simulation, a
hierarchy of caches and a single persistent key-value store are used to store
both observed minima across a molecule's equation of motion (EOM) and the
hundreds or thousands of partial trajectories calculated each second during a
parallel job. Unfortunately, if we scale the system the IO to the storage
hierarchy will quickly saturate both the storage and bandwidth capacity of a
single node, so we need more effective data management techniques, such as
cache management or load balancing across a cluster.

@@

In this paper, we design cache management policies for the ParSplice worker,
driven by a detailed analysis of the key-value accesses over the course of a
long running simulation across a variety of initial conditions.
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  This figure demonstrates that
small changes to \(\Delta\) can have a strong effect on the timing and
frequency with which new EOM minima are discovered and referenced.  The
ParSplice caches on each node are trimmed when memory pressure reaches a
threshold but the number of unique keys accessed in
Figure~\ref{fig:motivation-regimes} suggests that a small cache of EOM minima
should be sufficient.

% What is Mantle
We use the data management language and policy engine from the Mantle
paper~\cite{sevilla:sc15-mantle} to dynamically explore the effects of
different cache management strategies for the changing key-value workloads
generated by ParSplice.  Mantle was originally touted as a programmable file
system metadata load balancer, but we realize now that the collection of
abstractions designed for file systems was a control plane that improved
metadata access. So in this paper we refer to Mantle as a policy engine that
injects policies written in our data management language directly into a
running service ({\it e.g.} file system, key-value store, application) and show
how this approach is useful for reasoning about and designing different cache
management strategies in ParSplice. Developers write policies for ``when" they
want data moved and ``how much" of the data to move, then the framework
executes these policies whenever a decision needs to be made.  These
abstraction help developers unfamiliar with the domain quickly reason about,
develop, and deploy new policies that control temporal and spatial locality. We
show that Mantle:

@@

This last contribution is explored in
Sections~\S\ref{sec:cache-management-using-system-archiecture-knowledge}
and~\S\ref{sec:cache-management-using-domain-specific-knowledge}, where we try
a range of policies from different disciplines; but more importantly, in
Section~\S\ref{sec:relation-to-load-balancing}, we conclude that the collection
of policies we designed for ParSplice's cache management are very similar to
the policies used to load balance metadata in the Ceph file system (CephFS)
suggesting that there is potential for automatically adapting and generating
policies dynamically.

### 2017-11-09 paper/sections/2_parsplice-keyspace-analysis.tex
paper: 1st draft
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/parsplice.png}\\
\caption{The ParSplice architecture has a storage hierarchy of caches and a
dedicated cache node (purple boxes) backed by a persistent database (orange). A
splicer (S) tells worker nodes (W) to generate segments and workers employ
tasks (T) for more parallelization. We focus on the worker node's cache circled
in red, which facilitates communication and segment exchange between the worker
and its \label{fig:parsplice}} \end{figure}

@@

The computation can be parallelized by adding more workers or by adding worker
tasks to parallelize individual workers.  The workers are stateless and read
initial coordinates from the data store each time they begin generating
segments. Since worker tasks do not maintain their own history, they can end up
reading the same coordinates repeatedly. To mitigate the consequences of these
repeated reads, ParSplice provisions a hierarchy of nodes to act as caches that
sit in front of a single node persistent database.  Values are written to each
tier and reads traverse up the hierarchy until they find the data.

@@

We instrumented ParSplice with performance counters and keyspace counters.  The
performance counters track ParSplice progress while keyspace counters track
which keys are being accessed by the ParSplice ranks. Because the keyspace
counters have high overhead we only turn them on for the keyspace analysis.
The cache hierarchy is unmodified but for the persistent database node, we
replace BerkeleyDB on NFS with LevelDB on Lustre. Original ParSplice
experiments showed that BerkeleyDB's syncs caused reads/writes to bottleneck on
the persistent database. We also use Riak's customized
LevelDB\footnote{https://github.com/basho/leveldb} version, which comes
instrumented with its own set of performance counters.

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of
RAM\footnote{Empirically, we find this threshold works well for most
applications}. Note that this is an addition to the 30GB that ParSplice uses to
manage other ranks on the same node.  A single Cray node produced trajectories
that are \(5\times\) times longer than our 10 node CloudLab clusters and
\(25\times\) longer than UCSC's 10 node cluster. As a result, it reaches
different job phases faster and gives us a more comprehensive view of the
workload. The performance gains compared to the commodity clusters have more to
do with memory/PCI bandwidth than network.

The scalability experiment uses 1 splicer, persistent database node, and
in-memory database node and up to 2 workers. We scale up to 1024 tasks, which
spans 32 nodes and disable hyper-threading because we experience variability in
performance. For the rest of the experiments, we use 4 nodes, 1 splicer,
persistent database node, in-memory database node, worker, and up to 512 tasks.
The keyspace analysis is for the cache on the worker node, which is circled in
red in Figure~\ref{fig:parsplice}.

@@

\subsubsection*{Scalability} Figure~\ref{fig:methodology-keyspace} shows the
keyspace size (black annotations) and request load (bars) after a one hour run
with a different number of workers (\(x\) axis). While the keyspace size and
capacity is relatively modest the memory usage scales linearly with the number
of workers. This is a problem if we want to scale to Trinitite's 6000 cores.
Furthermore, the size of the keyspace also increases linearly with the length
of the run.  Extrapolating these results puts an 8 hour run across all 100
Trinitite nodes at 20GB for the cache.  This memory utilization easily eclipses
the 3\% threshold we set earlier, even without factoring in the memory usage
from other workers.

@@

\subsubsection*{Entropy increases over time} The reads per second in
Figure~\ref{fig:motivation-regimes} show that the number of requests decreases
and the number of active keys increases over time. The resulting key access
imbalance for the two growth rates in Figure~\ref{fig:motivation-regimes} are
shown in Figure~\ref{fig:methodology-keys}, where reads are plotted for each
unique state, or key, along the \(x\) axis. Keys are more popular than others
(up to \(5\times\)) because worker tasks start generating states with different
coordinates later in the run (this motivates
Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}).  The
growth rate, temperature, and number of workers have a predictable effect on
the structure of the keyspace.  Figure~\ref{fig:methodology-keys} shows that
the number of reads changes with different growth rates, but that the spatial
locality of key accesses is similar ({\it e.g.}, some keys are still
\(5\times\) more popular than others).  Figure~\ref{fig:motivation-regimes}
shows how entropy for different growth rates has temporal locality, as the
reads per second for \(\Delta_2\) looks like the reads per second for
\(\Delta_1\) stretched out along the time axis.  Trends also exist for
temperature and number of workers but are omitted here for space. This
structure means that we can learn the regimes and adapt the storage system
(this motivates Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}).

>>>>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/parsplice.png}\\
\caption{The ParSplice architecture has a storage hierarchy of caches and a
dedicated cache node (boxes) backed by a persistent database (DB). A splicer
(S) tells worker (W) to generate segments and workers employ tasks (T) for more
parallelization. We focus on the worker's cache (circled), which facilitates
communication and segment exchange between the worker and its
\label{fig:parsplice}}
\end{figure}

@@

The computation can be parallelized by adding more workers or by adding tasks
to parallelize individual workers.  The workers are stateless and read initial
coordinates from the data store each time they begin generating segments. Since
worker tasks do not maintain their own history, they can end up reading the
same coordinates repeatedly. To mitigate the consequences of these repeated
reads, ParSplice provisions a hierarchy of processes to act as caches that sit
in front of a single persistent database.  Values are written to each tier and
reads traverse up the hierarchy until they find the data.  Caches also reside
on the workers to service reads/writes from its tasks.

@@

We instrumented ParSplice with performance counters and keyspace counters.  The
performance counters track ParSplice progress while keyspace counters track
which keys are being accessed by the ParSplice ranks. Because the keyspace
counters have high overhead we only turn them on for the keyspace analysis.

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of
RAM\footnote{Empirically, we find this threshold works well for most
applications}. Note that this is an addition to the 30GB that ParSplice uses to
manage other ranks on the same node.  A single Cray node produced trajectories
that are \(5\times\) times longer than our 10 node CloudLab clusters and
\(25\times\) longer than our 10 node cluster at UCSC. As a result, it reaches
different job phases faster and gives us a more comprehensive view of the
workload. The performance gains compared to the commodity clusters have more to
do with memory/PCI bandwidth than network.

The scalability experiment uses 1 splicer, 1 persistent database, 1 cache
process, and up to 2 workers. We scale up to 1024 tasks, which spans 32 nodes
and disable hyper-threading because we experience unacceptable variability in
performance. For the rest of the experiments, we use 4 nodes, 1 splicer, 1
persistent database, 1 cache process, 1 worker, and up to 512 tasks.  The
keyspace analysis that follows is for the cache on the worker node, which is
circled in Figure~\ref{fig:parsplice}.  The cache hierarchy is unmodified but
for the persistent database node, we replace BerkeleyDB on NFS with LevelDB on
Lustre. Original ParSplice experiments showed that BerkeleyDB's syncs caused
reads/writes to bottleneck on the persistent database. We also use Riak's
customized LevelDB\footnote{https://github.com/basho/leveldb} version, which
comes instrumented with its own set of performance counters.

@@

\subsubsection*{Scalability} Figure~\ref{fig:methodology-keyspace} shows the
keyspace size (text annotations) and request load (bars) after a one hour run
with a different number of workers (\(x\) axis). While the keyspace size and
capacity is relatively modest the memory usage scales linearly with the number
of workers. This is a problem if we want to scale to Trinitite's 6000 cores.
Furthermore, the size of the keyspace also increases linearly with the length
of the run.  Extrapolating these results puts an 8 hour run across all 100
Trinitite nodes at 20GB for the cache.  This memory utilization easily eclipses
the 3\% threshold we set earlier, even without factoring in the memory usage
from other workers.

@@

\subsubsection*{Entropy increases over time} The reads per second in
Figure~\ref{fig:motivation-regimes} show that the number of requests decreases
and the number of active keys increases over time. The resulting key access
imbalance for the two growth rates in Figure~\ref{fig:motivation-regimes} are
shown in Figure~\ref{fig:methodology-keys}, where reads are plotted for each
unique state, or key, along the \(x\) axis. Keys are more popular than others
(up to \(5\times\)) because worker tasks start generating states with different
coordinates later in the run (this motivates
Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}).  The
growth rate, temperature, and number of workers have a predictable effect on
the structure of the keyspace.  Figure~\ref{fig:methodology-keys} shows that
the number of reads changes with different initial conditions (\(Delta\)), but
that the spatial locality of key accesses is similar ({\it e.g.}, some keys are
still \(5\times\) more popular than others).
Figure~\ref{fig:motivation-regimes} shows how entropy for different growth
rates has temporal locality, as the reads per second for \(\Delta_2\) looks
like the reads per second for \(\Delta_1\) stretched out along the time axis.
Trends also exist for temperature and number of workers but are omitted here
for space. This structure means that we can learn the regimes and adapt the
storage system (this motivates
Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}).

### 2017-11-09 paper/sections/3_methodology.tex
paper: 1st draft
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%  \item background: CephFS implementation
To explore dynamic cache management policies that change during the run, we use
a data management language and policy engine presented
in~\cite{sevilla:sc15-mantle}. The prototype in that paper was called Mantle
and it was originally built on the Ceph file system so administrators could
control file system metadata load balancing policies. We now refer to Mantle as
a policy engine that supports our data management language.  The basic premise
is that load balancing policies can be expressed with a simple API consisting
of ``when", ``where", and ``how much". ``when" controls how aggressive or
conservative the decisions are; ``where" lets the policy control how
distributed or concentrated the data should be; and ``how much" controls the
amount of data that should be sent.

@@

We extracted Mantle as a library and Figure~\ref{fig:mantle} shows how it is
linked into a service ({\it e.g.}, file system, key-value store, application).
Administrators write policies from different domains, like statistics, machine
learning, or storage systems, that that are embedded into the runtime. When the
service makes decisions it executes the administrator-defined policies for
when/where/how much and returns a decision. To do this, the service needs to be
modified to (1) provide an environment of metrics and (2) identify where
policies are set. These modification points are shown by the colored boxes in
Figure~\ref{fig:mantle} and described below.

@@

% policies themselves
\subsubsection{Policies Written as Callbacks} administrators write policies in
Lua that are executed whenever the service needs to make a data management
decision. We chose Lua for simplicity, performance, and portability; it is a
scripting language with simple syntax, which allows administrators to focus on
the policies themselves; it was designed as an embeddable language, so it is
lightweight and does less type checking; and it interfaces nicely with C/C++.
The pink box in Figure~\ref{fig:mantle} shows an example policy for the
``when()" callback in a distributed service, where the current server
(\texttt{whoami}) migrates load if it is has load (\texttt{>0.1}) and if its
neighbor server (\texttt{whoami + 1}) does not have load (\texttt{<0.1}). The
load is calculated using the metrics provided by the environment.

@@

Other examples metrics used for file system metadata load balancing, such as
memory pressure, are shown in Figure~\ref{fig:mantle}. The measurements and
exchange of metrics between servers is done by the service; Mantle in CephFS
leverages metrics from other servers collected using CephFS's heartbeats.

For time series metrics, the service passes array of \texttt{(timestamp,
value)} pairs to Mantle and the policies can iterate over the accesses. For
example, a policy that uses accesses to a certain directory to make migration
decisions collects that information using:

@@

% env of metrics
Using Mantle cluster metrics, we expose cache size, CPU utilization, memory
pressure of the worker node to the cache management policies. In
Section~\S\ref{sec:parsplice-keyspace-analysis} we only end up using the cache
size although the other metrics proved to be valuable debugging tools. Using
Mantle time series metrics, we expose accesses to the cache as a list of
\texttt{timestamp, keyid} pairs. In
Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}, we
explore a regime detection algorithm that uses this metric.

% where policies are made
We link Mantle directly into the worker cache circled in red in
Figure~\ref{fig:parsplice}. We put the ``when" and ``how much" callbacks
alongside code that checks for memory pressure. It is executed right before the
worker processes incoming and outgoing put/get transactions to the cache. As
stated previously, we do not use the ``where" part of Mantle because we focus
on a single node, but this part of the API will be used when we move the caches
and storage nodes to a key-values store back-end that has load balancing and key
redistribution.

>>>>

%  \item background: CephFS implementation
To explore dynamic cache management policies that change during the run, we use
the data management language and policy engine presented
in~\cite{sevilla:sc15-mantle}. The prototype in that paper was called Mantle
and it was originally built on the CephFS so administrators could control file
system metadata data management policies. We now refer to Mantle as a policy
engine that supports our data management language.  The basic premise is that
load balancing policies can be expressed with a simple API consisting of
``when", ``where", and ``how much". ``when" controls how aggressive or
conservative the decisions are; ``where" lets the policy control how
distributed or concentrated the data should be; and ``how much" controls the
amount of data that should be sent.

@@

We extracted Mantle as a library and Figure~\ref{fig:mantle} shows how it is
linked into a service.  Administrators write policies from whatever domain they
choose ({e.g.}, statistics, machine learning, storage system) and the policies
are embedded into the runtime by Mantle. When the service makes decisions it
executes the administrator-defined policies for when/where/how much and returns
a decision.  To do this, the service needs to be modified to (1) provide an
environment of metrics and (2) identify where policies are set. These
modification points are shown by the colored boxes in Figure~\ref{fig:mantle}
and described below.

@@

% policies themselves
\subsubsection{Policies Written as Callbacks} administrators write policies in
Lua that are executed whenever the service needs to make a data management
decision. We chose Lua for simplicity, performance, and portability; it is a
scripting language with simple syntax, which allows administrators to focus on
the policies themselves; it was designed as an embeddable language, so it is
lightweight and does less type checking; and it interfaces nicely with C/C++.
The ``callback" box in Figure~\ref{fig:mantle} shows an example policy for the
``when()" callback in a distributed service, where the current server
(\texttt{whoami}) migrates load if it is has load (\texttt{>0.1}) and if its
neighbor server (\texttt{whoami + 1}) does not have load (\texttt{<0.1}). The
load is calculated using the metrics provided by the environment.

@@

Other examples metrics used for file system metadata load balancing are shown
by the ``environment" box in Figure~\ref{fig:mantle}. The measurements and
exchange of metrics between servers is done by the service; Mantle in CephFS
leverages metrics from other servers collected using CephFS's heartbeats.

For time series metrics, the service passes an array of \texttt{(timestamp,
value)} pairs to Mantle and the policies can iterate over the accesses. For
example, a policy that uses accesses to a directory in a file system as a
metric for load collects that information using:

@@

% env of metrics
Using Mantle cluster metrics, we expose cache size, CPU utilization, and memory
pressure of the worker node to the cache management policies. In
Section~\S\ref{sec:parsplice-keyspace-analysis} we only end up using the cache
size although the other metrics proved to be valuable debugging tools. Using
Mantle time series metrics, we expose accesses to the cache as a list of
\texttt{timestamp, keyid} pairs. In
Section~\S\ref{sec:cache-management-using-domain-specific-knowledge}, we
explore a regime detection algorithm that uses this metric.

% where policies are made
We link Mantle directly into the worker cache circled in red in
Figure~\ref{fig:parsplice}. We put the ``when" and ``how much" callbacks
alongside code that checks for memory pressure. It is executed right before the
worker processes incoming and outgoing put/get transactions to the cache. As
stated previously, we do not use the ``where" part of Mantle because we focus
on a single node, but this part of the API will be used when we move the caches
and storage nodes to a key-values store back-end that uses key load balancing and
repartitioning.

### 2017-11-09 paper/sections/5_file-systems.tex
paper: 1st draft
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{Relation to File Systems}
\label{sec:relation-to-file-systems}

The code snippets in Figures~\ref{lua:parsplice} and~\ref{lua:cephfs} are the
policies used in ParSplice and CephFS, respectively.  ParSplice uses policies
to manage its caches and CephFS uses policies to control load balancing, but
they both can be expressed with Mantle.  From a high-level the ParSplice policy
trims the cache if the cache reaches a certain size {\it and} if it has already
absorbed the initial burstiness of the workload; the CephFS policy migrates
load if the metadata load is higher than the average load {\it and} the current
load has been overloaded for more than two iterations.

>>>>

\section{Relation to Load Balancing}
\label{sec:relation-to-load-balancing}

The code snippets in Figures~\ref{lua:parsplice} and~\ref{lua:cephfs} are the
policies used in ParSplice and CephFS, respectively.  ParSplice uses policies
to manage its caches and CephFS uses policies to control load balancing, but
they both can be expressed with our data management language.  From a
high-level the ParSplice policy trims the cache if the cache reaches a certain
size {\it and} if it has already absorbed the initial burstiness of the
workload; the CephFS policy migrates load if the metadata load is higher than
the average load {\it and} the current load has been overloaded for more than
two iterations.
